\bf Summary

### 2025-02-13 paper/paper.qmd
make code echo and fix referencing of in-text author citations. For preprint branch only

The `stations` data set included in the `traveltime` package is a 563 row, 2 column `matrix` containing the longitude (`x`) and latitude (`y`) of all LRT and MRT station exits in Singapore from Land Transport Authority @singdata:

```{r}
#| label: show-stations
library(traveltime)
head(stations)
```

@@

```{r }
#| label: show-friction-surface-raster
friction_singapore
```

@@

```{r}
#| label: calculate-result
trave_time_singapore <- calculate_travel_time(
  friction_surface = friction_singapore,
  points = stations
)

>>>>

The `stations` data set included in the `traveltime` package is a 563 row, 2 column `matrix` containing the longitude (`x`) and latitude (`y`) of all LRT and MRT station exits in Singapore from Land Transport Authority [@singdata]:

```{r}
#| echo: true
#| label: show-stations
library(traveltime)
head(stations)
```

@@

```{r }
#| echo: true
#| label: show-friction-surface-raster
friction_singapore
```

@@

```{r}
#| echo: true
#| label: calculate-result
trave_time_singapore <- calculate_travel_time(
  friction_surface = friction_singapore,
  points = stations
)

### 2025-02-13 paper/paper.tex
make code echo and fix referencing of in-text author citations. For preprint branch only

The \texttt{stations} data set included in the \texttt{traveltime}
package is a 563 row, 2 column \texttt{matrix} containing the longitude
(\texttt{x}) and latitude (\texttt{y}) of all LRT and MRT station exits
in Singapore from Land Transport Authority \citet{singdata}:

@@

@@

>>>>

The \texttt{stations} data set included in the \texttt{traveltime}
package is a 563 row, 2 column \texttt{matrix} containing the longitude
(\texttt{x}) and latitude (\texttt{y}) of all LRT and MRT station exits
in Singapore from Land Transport Authority \citep{singdata}:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(traveltime)}
\FunctionTok{head}\NormalTok{(stations)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{friction\_singapore}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{trave\_time\_singapore }\OtherTok{\textless{}{-}} \FunctionTok{calculate\_travel\_time}\NormalTok{(}
  \AttributeTok{friction\_surface =}\NormalTok{ friction\_singapore,}
  \AttributeTok{points =}\NormalTok{ stations}
\NormalTok{)}

\NormalTok{trave\_time\_singapore}
\end{Highlighting}
\end{Shaded}
